---
title: "Data processing pipeline - Uebung 2"
author: "NACHNAME, V., NACHNAME, V., NACHNAME, V."
output: html_document
date: "`r Sys.Date()`"
---

# Setup

```{r}
#| message: false
library(tidyverse)
```

# A. Data dictionary

Included variables: 

- id (identification)
- block (experimental block)
- trial (experimental trial)
- detected_orienation (the orientation from grating participants were instructed to detect LEFT or RIGHT)
- imagined_orientation (the orientation from grating participants were instructed to imagine LEFT or RIGHT)
- condition (signal absent o present)
- visLevel (visibility of the stimulus in %, technically, the probability that a pixel was part of the image vs noise.)
- response (what participants answered, right key: stimulus was present, left: absent)
- corr (whether answer was correct, 1: correct, 0: not correct)
- rt (response time in seconds)
- vividness_rating (the vividness rating (1-5) given at the end of each block in which there was imagery involved (i.e. imagine left or right blocks), 1: low, 5: high)
- compliance (at the end of each block, participants were asked what they imagined: right grating (press right arrow), left grating (press left), or nothing (press down))
- complied (compliance compared to the actually imagined_orientation to check whether they complied to the instructions
- congruency (if the imagined and the presented orientation align: congruent, if not: incongruent, if not applicable: none)

INSERT DATA DICTIONARY OF THE ABOVE VARIABLES WITH THE FOLLOWING COLUMNS:

| variable | label | type | values | source | transformations | universe | skip_logic |

(see <https://www.tablesgenerator.com/markdown_tables> for help)


# B. Data cleaning plan

DATA SHOULD HAVE THE VARIABLES DEFINED IN DATA DICTIONARY ABOVE

INSERT DATA CLEANING PLAN, e.g.

- Step
- Step
    - Substep 
- Step 
    - Substep 
    - Substep 
    

# C. Automated read in and cleaning

Read in raw data and clean it according to data cleaning plan.
Write all data in one dataset `d_raw`.
(set to `eval: false` as soon as clean dataset is saved)

```{r}
#| eval: true
# d_raw <- INSERT DATA READ-IN AND CLEANING CODE (DATA IN FOLDER data/raw)

```


Save cleaned data file as `dijkstra_data.csv`-file in folder `data`. 
(set to `eval: false` as soon as clean dataset is saved)

```{r}
#| eval: false
write.csv(d_raw, "data/dijkstra_data.csv", row.names = FALSE)
rm(d_raw) # removes d_raw dataset from environment

```

Read in clean data.
(set to `eval: true` to use the cleaned, saved dataset for further use)

```{r}
#| eval: false
d <- read.csv("data/dijkstra_data.csv")
```


# D. Descriptive Analysis

```{r}
# insert descriptive analysis to generate variables used in the text below
n = 999 # number of all participants
accuracy = 999 # overall accuracy in trials
accuracy_congruent = 999 # accuracy in congruent trials
accuracy_incongruent = 999 # accuracy in incongruent trials
```

`r n` participants were included.
Participants showed and accuracy of `r accuracy`, with a higher/lower accuracy in the congruent condition (`r accuracy_congruent`) compared to the incongruent condition (`r accuracy_incongruent`).

# E. Visualisation

Research question: INSERT RESEARCH QUESTION

Target audience: SCIENTIFIC EXPERTS / GENERAL PUBLIC (SCIENCE COMMUNICATION) / STAKEHOLDER (choose one)

Aim of the visualisation: DIAGNOSTIC PLOT / SHOW RESULT


```{r}
#  if necessary: insert preprocessing for visualization
```


```{r}
# insert code for data visualisation
# visualisation must include:
# - data distribution info (error bars, quantiles, density)
# - at least one visible data point from each participant (raw data, or could also be a mean of participants' responses)
# - different colors (greys are ok)
# - cleanly labelled axes
# - title (must contain the research question)
# - caption (must contain target audience and aim of visualisation)
# - a changed theme
# - optional: altered font, adapted theme

```


Save plot (set to `eval: true` when adapted for your use)

```{r}
#| eval: false
ggsave(filename = "plots/NAME.JPG",
       plot = get_last_plot(), #saves last plot, can also be an object name from environment e.g. p1
       width = 7,
       height = 7,
       units = "cm", # can also be "mm" for millimeters, "px" for pixels, "in" for inches
       dpi = 300) # plot resolution
```

